Clustering: A pipeline to analyse time-course gene expression data

### 2019-05-08 scripts/03_clustering.Rmd
More and better texts

both_labels = data.frame("kmeans"=kmeans_labels, "scored"=labels)
# Create another cluster.
#both_labels[is.na(both_labels)] = 21
confusion_matrix = table(both_labels)
text = as.matrix(as.character(confusion_matrix))
dim(text) = dim(confusion_matrix)
NMF::aheatmap(confusion_matrix, treeheight=0, main="Confusion matrix", 
	      border=list(cell=TRUE), txt=text, legend=FALSE, Rowv=FALSE,
	      Colv=FALSE)
labels = scores_and_labels$labels
labels = unlist(labels[!is.na(labels)])

@@

Now, let us look more in detail some specific clusters. Cluster 4 seems
particularly interesting: it captures genes with strong differences between
the differant influenza treatments and the control, while the control remains
relatively flat.

@@

```{r}
cluster_to_plot = 4
genes_to_plot =  names(labels[labels == cluster_to_plot])
```

```{r fig.width=6, fig.height=8}
layout(matrix(c(1,2),nrow=1), widths=c(1, 2))

>>>>

both_labels = data.frame("kmeans"=kmeans_labels, "scored"=labels)
# Create another cluster.
#both_labels[is.na(both_labels)] = 21
confusion_matrix = table(both_labels)
text = as.matrix(as.character(confusion_matrix))
dim(text) = dim(confusion_matrix)
NMF::aheatmap(confusion_matrix, treeheight=0, main="Confusion matrix", 
	      border=list(cell=TRUE), txt=text, legend=FALSE, Rowv=NA,
	      Colv=NA)
labels = scores_and_labels$labels
labels = unlist(labels[!is.na(labels)])

@@

Now, let us look more in detail some specific clusters. Cluster 8 seems
particularly interesting: it captures genes with strong differences between
the differant influenza treatments and the control, while the control remains
relatively flat.

@@

```{r}
cluster_to_plot = 8
genes_to_plot =  names(labels[labels == cluster_to_plot])
```

```{r fig.width=6, fig.height=8}
layout(matrix(c(1,2),nrow=1), widths=c(1.5, 2))
